Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-04 WSSSPE3/report/WSSSPE3_review.tex
question about lightning talks section
Acknowledge support.
Section 3: Keynote: Response to Dan's comment after Matt explained.

Turk said that sustaining scientific software really meant to him
conducting scientific inquiries, often by some specific software, and sustaining
the people we care about, our careers, and the future of our fields. According
to Turk, we all have an invested stake in sustaining scientific software. Again
it came down to the top-down versus bottom-up notion that we can have anointed
specific software packages to be sustained at the expense of new grassroots
developments. \katznote{I don't understand this last sentence.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lightning Talks} \label{sec:lightning}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{need to update for WSSSPE3}
\begin{comment}
\note{
\href{http://wssspe.researchcomputing.org.uk/wssspe3/agenda/}{Slides.}}
\end{comment}

@@

Work by Katz was supported by the National Science Foundation while working at
the Foundation. Any opinion, finding, and conclusions or recommendations
expressed in this material are those of the author(s) and do not necessarily
reflect the views of the National Science Foundation.

>>>>

Turk said that sustaining scientific software really meant to him conducting
scientific inquiries, often by some specific software, and sustaining the people
we care about, our careers, and the future of our fields. According to Turk, we
all have an invested stake in sustaining scientific software. Hence, having
``sustained'' projects can suffocate new projects, for which we need to keep a
lookout.
%This is a straw man concept, but it's something to look out for, since organizations will act in their own interest.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lightning Talks} \label{sec:lightning}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{need to update for WSSSPE3}
\todo{KEN: Should these be bolded?}
\begin{comment}
\note{
\href{http://wssspe.researchcomputing.org.uk/wssspe3/agenda/}{Slides.}}
\end{comment}

@@

Work by Katz was supported by the National Science Foundation while working at
the Foundation. Any opinion, finding, and conclusions or recommendations
expressed in this material are those of the author(s) and do not necessarily
reflect the views of the National Science Foundation. Choi's work is supported
in part by the National Science Foundation research grant DMS-1522687 and
a WSSSPE3 travel award.
